---
title: "Report with params"
author: "Marina Reixachs Solé"
date: "`r Sys.Date()`"
output: html_document
params:
    input: ''
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(formattable)
```

# Sample report with parameters from command line

The `.Rmd` file is executed as the following:

`Rscript -e "rmarkdown::render('template_report_cmdline_params.Rmd',params=list('sample_file.tsv'))"`

If there is any trouble locating pandoc, first identify your pandoc location:

`Sys.getenv("RSTUDIO_PANDOC")`

Then add the path from that command to your R environment prior to rendering the Rmarkdown:

`R -e "Sys.setenv(RSTUDIO_PANDOC='path_to_pandoc'); rmarkdown::render('template_report_cmdline_params.Rmd',params=list('sample_file.tsv'))"`


## Read file

```{r read_tsv}
df = read.delim(file = params$input)
```

## Report table

```{r table}
formattable::formattable(df, list(
  Murder =color_tile("white", "firebrick"),
  Rape = color_tile("white", "firebrick"),
  UrbanPop = formatter("span", style = x ~ ifelse(x > 60,
    style(color = "#DE6E4B", font.weight = "bold"), NA)),area(col = c(Assault)) ~ normalize_bar("#7FD1B9", 0.6)
))
```

